SunPy - Python for Solar Physics

### 2014-01-27 3-3-HELIO.tex
More edits to HELIO section

Desired time range and event type
>>> tstart = '2011-06-07T06:00:00'
>>> tend = '2011-06-07T12:00:00'
>>> event_type = 'cme'

Obtain from all the catalogues these which name contain our event of interest
>>> catalogues = hc.get_table_names()
>>> catalogues_event = [l[0] for l in catalogues if event_type in l[0]]
>>> print catalogues_event
******** This need to be added!

@@

>>>>

Desired time range and event type
>>> tstart, tend = '2011-06-07T06:00:00', '2011-06-07T12:00:00'
>>> event_type = 'cme'

Obtain from all the catalogues these which name contain our event of interest
>>> catalogues = hc.get_table_names()
>>> catalogues_event = [l[0] for l in catalogues if event_type in l[0]]
>>> print catalogues_event
['hi_cme_list', 'cactus_stereoa_cme', 'icme_earth_cycle23', 'cactus_cme_list', '
goes_flare_no_sep_radio_cme', 'ulysses_swoops_icme', 'cme_forbush_event', 'seeds
_cme', 'cme_inner_heliosphere', 'mars_earth_icme', 'stereo_hi_cme', 'cactus_ster
eob_cme', 'cactus_soho_cme', 'lasco_cme_list', 'cactus_stb_cme_list', 'cactus_so
ho_cme_list', 'halo_cme_flare_magnetic_storm', 'lasco_cme_cat', 'cactus_sta_cme_
list', 'stereoa_impactplastic_icme', 'stereob_impactplastic_icme', 'soho_lasco_c
me', 'stereo_impactplastic_icme', 'wind_typeii_soho_cme']

@@

Additional HELIO services will be supported in the future by SunPy.
